Functional pant indicators - wetland, indicator documentation

### 2023-05-10 functional_plant_indicators_wetland.Rmd
wrapping up the markdowns for seminat and wetland

```{r, include = F}
# Data from cache
wetland.ref.cov<-readRDS(paste0(here::here(), "/data/cache/wetland.ref.cov.RDS"))
#load("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/FPI_output large files for markdown/ref_lists_wetland.RData")
```

@@

### pH
par(mfrow=c(4,4))
## V1s
# V1-C-1
plot(density( as.matrix(wetland.ref.cov[['Soil_reaction_pH']][,c("V1-C1a","V1-C1b","V1-C1c","V1-C1d","V1-C1e")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V1-C1',xlab='pH value')
points(density(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original)),
       col="red")

@@

## V2s
# V2-C-1
plot(density( as.matrix(wetland.ref.cov[['Soil_reaction_pH']][,c("V2-C1a","V2-C1b")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V2-C1',xlab='pH value')
points(density(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original)),
       col="red")

@@

### Nitrogen
par(mfrow=c(4,4))
## V1s
# V1-C-1
plot(density( as.matrix(wetland.ref.cov[['Nitrogen']][,c("V1-C1a","V1-C1b","V1-C1c","V1-C1d","V1-C1e")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V1-C1',xlab='Nitrogen value')
points(density(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original)),
       col="red")

@@

## V2s
# V2-C-1
plot(density( as.matrix(wetland.ref.cov[['Nitrogen']][,c("V2-C1a","V2-C1b")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V2-C1',xlab='Nitrogen value')
points(density(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original)),
       col="red")

>>>>

```{r, include = F}
# Data from cache
wetland.ref.cov<-readRDS(paste0(here::here(), "/data/cache/wetland.ref.cov.RDS"))

#load("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/FPI_output large files for markdown/ref_lists_wetland.RData")
```

@@

### pH
par(mfrow=c(2,4))
## V1s
# V1-C-1
plot(density( as.matrix(wetland.ref.cov[['Soil_reaction_pH']][,c("V1-C1a","V1-C1b","V1-C1c","V1-C1d","V1-C1e")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V1-C1',xlab='pH value')
points(density(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original)),
       col="red")

@@

par(mfrow=c(2,4))
## V2s
# V2-C-1
plot(density( as.matrix(wetland.ref.cov[['Soil_reaction_pH']][,c("V2-C1a","V2-C1b")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V2-C1',xlab='pH value')
points(density(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="pH1" & res.wetland$fp_ind=="pH1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original)),
       col="red")

@@

### Nitrogen
par(mfrow=c(2,4))
## V1s
# V1-C-1
plot(density( as.matrix(wetland.ref.cov[['Nitrogen']][,c("V1-C1a","V1-C1b","V1-C1c","V1-C1d","V1-C1e")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V1-C1',xlab='Nitrogen value')
points(density(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V1-C-1",]$original)),
       col="red")

@@

par(mfrow=c(2,4))
## V2s
# V2-C-1
plot(density( as.matrix(wetland.ref.cov[['Nitrogen']][,c("V2-C1a","V2-C1b")]) ,na.rm=T),
     xlim=c(1,7), type="l", main='V2-C1',xlab='Nitrogen value')
points(density(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original,
       rep(0,length(res.wetland[res.wetland$fp_ind=="Nitrogen1" & res.wetland$fp_ind=="Nitrogen1" & res.wetland$kartleggingsenhet_1m2=="V2-C-1",]$original)),
       col="red")
